\bf Tearing Mode Dynamics in Tokamak Plasmas

### 2021-11-25 Documentation/TearingModeTheory.tex
Latest version

\subsection{Derivation of Linear Layer Equations}\label{s5.3}
Suppose that the system is perturbed by a tearing mode with $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
\begin{align}\label{e295}
\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
U(\hat{x},\zeta,\hat{t}) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
\end{align}
where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear layer equations:
\begin{align}\label{e301}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} \\[0.5ex]
&\phantom{=}
+S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
+ S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\nonumber\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e304}
\end{align}
Here, 
\begin{equation}
\tau_H = \frac{L_s}{m\,V_A}
\end{equation}
is the {\em hydromagnetic time}, 
\begin{equation}
\omega_E = \left(\frac{m}{r_s}\right)V_E(r_s)
\end{equation}
  the 
{\em E-cross-B frequency}, 
\begin{equation}
\omega_{\ast\,e} = -\left(\frac{\tau}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
\end{equation}
  the {\em electron diamagnetic
frequency},
\begin{align}
  \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
  \end{align}
    the {\em ion diamagnetic
frequency}, 
\begin{equation}
S=\frac{\tau_R}{\tau_H}
\end{equation}
 the {\em Lundquist number}, 
\begin{equation}\label{e317a}
\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
\end{equation}
 the
{\em resistive diffusion time}, 
\begin{equation}\label{e318a}
\tau_\varphi
= \frac{r_s^{\,2}}{\chi_\varphi}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
\end{equation} 
the {\em toroidal momentum confinement time}, and 
\begin{equation}
\tau_\perp = \frac{r_s^{\,2}}{D_\perp}
\end{equation}
 the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel$.

@@

\subsection{Determination of Linear Growth-Rates}\label{s6.3}
Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, let us again suppose that there are two layers in $p$ space (i.e., Fourier space). The
small-$p$ layer turns out to be of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
$|\hat{\gamma}|\ll 1$, the condition for the separation of the layer solution into two layers (i.e., that the width of the small-$p$ layer is less than that of the large-$p$ layer) is always satisfied. The large-$p$ layer is governed by the equation
\begin{equation}\label{e355}
\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y_e =0,
\end{equation}
where 
\begin{align}
A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
-{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
\end{align}
Here, $Q_\ast = S^{1/3}\,\omega_\ast\,\tau_H$, where
\begin{equation}
\omega_\ast = -\frac{m}{r_s}\frac{1}{e\,n_0\,B_z}\left.\frac{dp}{dr}\right|_{r_s}.
\end{equation}
In the following, $\omega_\ast$ is assumed to be positive. The boundary conditions on Equation~(\ref{e355}) are
that $Y_e$ is bounded as $p\rightarrow\infty$, and
\begin{equation}\label{e359}
Y_e(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
\end{equation}
as $p\rightarrow 0$.

@@

It is helpful to define the reduced island width
\begin{equation}\label{e456}
w = \frac{W}{4} = (L_s\,R_0\,\hat{\mit\Psi}_s)^{1/2}.
\end{equation}
[See Equation~(\ref{e355s}).]
It is assumed that $\delta\ll w\ll r_s$, where $\delta$ is the linear layer width. Let $\hat{w}= w/r_s$.  Reusing the analysis of Section~\ref{linear},
in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface) we find that 
\begin{align}
\hat{\psi} &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \hat{R}_0\,\hat{\mit\Psi}_s\,\cos\zeta,\\[0.5ex]
\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
J& \rightarrow -\frac{2}{q_s\hat{R}_0} + \frac{1}{\hat{L}_s}.
\end{align}
Here, $\omega = \hat{\omega}\,V_A/r_s$ is the helical phase velocity of the island chain in the
laboratory frame,
\begin{equation}
s = {\rm sgn}(\hat{x}),
\end{equation}
and 
\begin{equation}
\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
there.

\subsection{Rescaled Four-Field Model}\label{s8.2}
Let
\begin{align}
X &= \frac{\hat{x}}{\hat{w}},\\[0.5ex]
T &= \omega_\ast\,t.
\end{align}
It follows that $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
rescaled fields ${\mit\Psi}(X,\zeta,T)$, ${\mit\Phi}(X,\zeta,T)$, ${\cal N}(X,\zeta,T)$,
${\cal V}(X,\zeta,T)$, and ${\cal J}(X,\zeta,T)$, where
\begin{align}
\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
\phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
N &= \left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\cal N},\\[0.5ex]
V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
J & =-\frac{2}{q_s \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
\end{align}
The four-field model specified in Section~\ref{fourf} rescales to give
\begin{align}\label{e469}
\frac{d(\ln \hat{w}^2)}{dT}\,\cos\zeta &= \left\{{\mit\Phi}-\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,{\cal N}, {\mit\Psi}\right\}
+ \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J},\\[0.5ex]
\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},\partial_X{\mit\Phi}\right\}
+ \{{\cal J},{\mit\Psi}\}+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\label{e470}\\[0.5ex]
\frac{\partial {\cal N}}{\partial T} &= \{{\mit\Phi}, {\cal N}\} + \{{\cal V},{\mit\Psi}\} + \epsilon_d\,\epsilon_n\,\{{\cal J},{\mit\Psi}\}\nonumber\\[0.5ex]&\phantom{=}
+ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\label{e471}\\[0.5ex]
\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\label{e472}\\[0.5ex]
\partial_X^{\,2}{\mit\Psi} &= 1+ \epsilon_\beta\,\epsilon_d\,{\cal J}.\label{e473}
\end{align}
Here,  $\partial_X\equiv \partial/\partial X$, 
\begin{equation}
\{A,B\} \equiv \frac{\partial A}{\partial X}\,\frac{\partial B}{\partial\zeta} - \frac{\partial A}{\partial \zeta}\,\frac{\partial B}{\partial X},
\end{equation}
and we have set
\begin{equation}
\hat{E}_\parallel = \left(\frac{2}{q_s\hat{R}_0}-\frac{1}{\hat{L}_s}\right)\eta_\parallel.
\end{equation}
Furthermore,
\begin{align}
\epsilon_d &= \left(\frac{L_s}{L_n}\right)\left(\frac{d_\beta}{w}\right)^2,\\[0.5ex]
\epsilon_\beta &= c_\beta^{\,2},\\[0.5ex]
\epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\label{e481}\\[0.5ex]
\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\label{e482}\\[0.5ex]
\epsilon_D &= \frac{D_\perp}{\omega_\ast\,w^2}.
\end{align}
Finally,
\begin{equation}
\frac{1}{L_n}= -\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}
\end{equation}
is the {\em density gradient scalelength}\/  at the resonant surface, 
and the critical reduced island width, $w_c$, is defined in Equation~(\ref{wcdef}).

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{align}
In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

>>>>

\subsection{Derivation of Linear Layer Equations}\label{s5.3}
Suppose that the system is perturbed by a tearing mode with $m$ periods in the poloidal direction, and
$n$ periods in the toroidal direction. In accordance with Equations~(\ref{e287})--(\ref{e290}), and (\ref{e292})--(\ref{e293}), we can write
\begin{align}\label{e295}
\hat{\psi}(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
U(\hat{x},\zeta,\hat{t}) &=  \hat{\nabla}^2\tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e300}
\end{align}
where $\hat{t}=V_A\,t/r_s$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Equations~(\ref{e294})--(\ref{e300}) into the four-field model, (\ref{e264})--(\ref{e269}), and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear layer equations:
\begin{align}\label{e301}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi} \\[0.5ex]
&\phantom{=}
+S^{-1}\,P_\parallel\!\left(m\,\omega_{\ast\,e}\,\tau_H\,\hat{x}\,\tilde{\psi}-\frac{m}{\hat{L}_s}\,\hat{x}^2\,\tilde{N}\right)
+ S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\nonumber\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e304}
\end{align}
Here, 
\begin{equation}
\tau_H = \frac{L_s}{m\,V_A}
\end{equation}
is the {\em hydromagnetic time}, 
\begin{equation}
\omega_E = \left(\frac{m}{r_s}\right)V_E(r_s)
\end{equation}
  the 
{\em E-cross-B frequency}, 
\begin{equation}
\omega_{\ast\,e} = -\left(\frac{\tau}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
\end{equation}
  the {\em electron diamagnetic
frequency},
\begin{align}\label{omegai}
  \omega_{\ast\,i} &= \left(\frac{1}{1+\tau}\right)\left(\frac{m}{r_s}\right)V_\ast(r_s)
  \end{align}
    the {\em ion diamagnetic
frequency}, 
\begin{equation}
S=\frac{\tau_R}{\tau_H}
\end{equation}
 the {\em Lundquist number}, 
\begin{equation}\label{e317a}
\tau_R = \frac{\mu_0\,r_s^{\,2}}{\eta_\parallel}
\end{equation}
 the
{\em resistive diffusion time}, 
\begin{equation}\label{e318a}
\tau_\varphi
= \frac{r_s^{\,2}}{\chi_\varphi}=\frac{r_s^{\,2}\,n_0\,m_i}{\mu_\perp(r_s)}
\end{equation} 
the {\em toroidal momentum confinement time}, and 
\begin{equation}
\tau_\perp = \frac{r_s^{\,2}}{D_\perp}
\end{equation}
 the {\em particle/energy confinement time}. Furthermore, $P_\varphi = \tau_R/\tau_\varphi$, $P_\perp = \tau_R/\tau_\perp$, 
$P_\parallel=\tau_R/\tau_\parallel$, and $\tau_\parallel =r_s^{\,2}/D_\parallel$.

@@

\subsection{Determination of Linear Growth-Rates}\label{s6.3}
Reusing the analysis of Sections~\ref{s5.6} and \ref{scp}, let us again suppose that there are two layers in $p$ space (i.e., Fourier space). The
small-$p$ layer turns out to be of width $|\hat{\gamma}|^{1/2}$, where $\hat{\gamma} = S^{1/3}\,\gamma\,\tau_H$. Given that we are effectively assuming that
$|\hat{\gamma}|\ll 1$, the condition for the separation of the layer solution into two layers (i.e., that the width of the small-$p$ layer is less than that of the large-$p$ layer) is always satisfied. The large-$p$ layer is governed by the equation
\begin{equation}\label{e355}
\frac{d^{\,2} Y_e}{dp^2} - \frac{A(p)}{\tilde{B}(p)} \,Y_e =0,
\end{equation}
where 
\begin{align}
A(p) &= (1+\lambda_e)\left(\frac{\tau}{1+\tau}\right)\left(1+ \frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast^{\,2}
-{\rm i}\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,(P_\varphi+P_\perp)\,p^2\nonumber\\[0.5ex]
&\phantom{=} + P_\varphi\,P_\perp\,p^4,\\[0.5ex]
\tilde{B}(p)&= P_\perp - {\rm i}\,(1+\lambda_e)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right)Q_\ast\,D^2 +\left(\frac{1+\tau}{\tau}\right)\left(1+\frac{\lambda_e\,\tau}{1+\tau}\right) D^2\,P_\varphi\,p^2.
\end{align}
Here, $Q_\ast = S^{1/3}\,\omega_\ast\,\tau_H$, where
\begin{equation}\label{omega}
\omega_\ast = -\frac{m}{r_s}\,V_\ast(r_s)= -\frac{m}{r_s}\frac{1}{e\,n_0\,B_z}\left.\frac{dp}{dr}\right|_{r_s}.
\end{equation}
In the following, $\omega_\ast$ is assumed to be positive. The boundary conditions on Equation~(\ref{e355}) are
that $Y_e$ is bounded as $p\rightarrow\infty$, and
\begin{equation}\label{e359}
Y_e(p)= Y_0\left[1-\frac{\hat{\mit\Delta}\,p}{\pi\,\hat{\gamma}} + {\cal O}(p^2)\right]
\end{equation}
as $p\rightarrow 0$.

@@

It is helpful to define the reduced island width
\begin{equation}\label{e456}
w = \frac{W}{4} = (L_s\,R_0\,\hat{\mit\Psi}_s)^{1/2}.
\end{equation}
[See Equation~(\ref{e355s}).]
It is assumed that $\delta\ll w\ll r_s$, where $\delta$ is the linear layer width. Let $\hat{w}= w/r_s$.  Reusing the analysis of Section~\ref{linear},
in the limit $|\hat{x}|/\hat{w}\gg 1$ (i.e., many island widths from the resonant surface) we find that 
\begin{align}
\hat{\psi} &\rightarrow \frac{\hat{x}^{\,2}}{2\,\hat{L}_s} + \hat{R}_0\,\hat{\mit\Psi}_s\,\cos\zeta,\\[0.5ex]
\phi &\rightarrow \left(\frac{\hat{\omega}}{m}- \hat{V}_E\right)\hat{x} - \frac{s}{4}\,\hat{V}_E'\,\hat{x}^{\,2},\\[0.5ex]
N &\rightarrow -\hat{V}_\ast\,\hat{x},\\[0.5ex]
V&\rightarrow \hat{V}_\parallel,\\[0.5ex]
J& \rightarrow -\frac{2}{q_s\hat{R}_0} + \frac{1}{\hat{L}_s}.
\end{align}
Here, $\omega = \hat{\omega}\,V_A/r_s$ is the helical phase velocity of the island chain in the
laboratory frame,
\begin{equation}
s = {\rm sgn}(\hat{x}),
\end{equation}
and 
\begin{equation}
\hat{V}_E' = \frac{1}{V_A}\left[r\,\frac{dV_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The parameter $\hat{V}_E'$ is introduced  into the analysis in order to take into account the fact that the plasma rotation profile in the outer region develops a
gradient discontinuity at the resonant surface in response to the nonlinear localized electromagnetic torque that develops
at the surface.

\subsection{Rescaled Four-Field Model}\label{s8.2}
Let
\begin{align}
X &= \frac{\hat{x}}{\hat{w}},\\[0.5ex]
T &= \omega_\ast\,t.
\end{align}
It follows that $|X|\sim {\cal O}(1)$ in the immediate vicinity of the island chain. It is helpful to define the
rescaled fields ${\mit\Psi}(X,\zeta,T)$, ${\mit\Phi}(X,\zeta,T)$, ${\cal N}(X,\zeta,T)$,
${\cal V}(X,\zeta,T)$, and ${\cal J}(X,\zeta,T)$, where
\begin{align}
\hat{\psi} &= \left(\frac{\hat{w}^{\,2}}{\hat{L}_s}\right){\mit\Psi},\label{e466}\\[0.5ex]
\phi &=\left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\mit\Phi},\\[0.5ex]
N &= \left(\frac{\hat{\omega}_\ast\,\hat{w}}{m}\right){\cal N},\\[0.5ex]
V&= \hat{V}_\parallel + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,c_\beta^{\,2}}\right){\cal V},\\[0.5ex]
J & =-\frac{2}{q_s \hat{R}_0} + \frac{1}{\hat{L}_s} + \left(\frac{\hat{L}_s\,\hat{\omega}_\ast^{\,2}}{m^2\,\hat{w}^{\,2}}\right){\cal J}.
\end{align}
The four-field model specified in Section~\ref{fourf} rescales to give
\begin{align}\label{e469}
\frac{d(\ln \hat{w}^2)}{dT}\,\cos\zeta &= \left\{{\mit\Phi}-\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,{\cal N}, {\mit\Psi}\right\}
+ \epsilon_\beta\,\epsilon_d\,\epsilon_\eta\,{\cal J},\\[0.5ex]
\frac{\partial(\partial_X^{\,2}\,{\mit\Phi})}{\partial T} &= \partial_X\!\!\left\{{\mit\Phi} + \frac{{\cal N}}{1+\tau},\partial_X{\mit\Phi}\right\}
+ \{{\cal J},{\mit\Psi}\}+ \epsilon_\chi \,\partial_X^{\,4}\!\left({\mit\Phi} + \frac{{\cal N}}{1+\tau}\right),\label{e470}\\[0.5ex]
\frac{\partial {\cal N}}{\partial T} &= \{{\mit\Phi}, {\cal N}\} + \{{\cal V},{\mit\Psi}\} + \epsilon_d\,\epsilon_n\,\{{\cal J},{\mit\Psi}\}\nonumber\\[0.5ex]&\phantom{=}
+ \epsilon_D \!\left[\left(\frac{w}{w_c}\right)^4\,\{\{{\cal N},{\mit\Psi}\}, {\mit\Psi}\}+\partial_X^{\,2}{\cal N}\right],\label{e471}\\[0.5ex]
\epsilon_d\,\frac{\partial {\cal V}}{\partial T} &= \epsilon_d\,\{{\mit\Phi},{\cal V}\}+\{{\cal N}, {\mit\Psi}\} + \epsilon_d\,\epsilon_\chi\,\partial_X^{\,2} {\cal V},\label{e472}\\[0.5ex]
\partial_X^{\,2}{\mit\Psi} &= 1+ \epsilon_\beta\,\epsilon_d\,{\cal J}.\label{e473}
\end{align}
Here,  $\partial_X\equiv \partial/\partial X$, 
\begin{equation}
\{A,B\} \equiv \frac{\partial A}{\partial X}\,\frac{\partial B}{\partial\zeta} - \frac{\partial A}{\partial \zeta}\,\frac{\partial B}{\partial X},
\end{equation}
and we have set
\begin{equation}
\hat{E}_\parallel = \left(\frac{2}{q_s\hat{R}_0}-\frac{1}{\hat{L}_s}\right)\eta_\parallel.
\end{equation}
Furthermore,
\begin{align}
\epsilon_d &= \left(\frac{L_s}{L_n}\right)^2\left(\frac{d_\beta}{w}\right)^2,\label{e479}\\[0.5ex]
\epsilon_\beta &= c_\beta^{\,2},\label{e480}\\[0.5ex]
\epsilon_n&= \left(\frac{L_n}{L_s}\right)^2,\\[0.5ex]
\epsilon_\eta &= \frac{\eta_\parallel}{\mu_0\,\omega_\ast\,w^2},\label{e481}\\[0.5ex]
\epsilon_\chi &= \frac{\chi_\phi}{\omega_\ast\,w^2},\label{e482}\\[0.5ex]
\epsilon_D &= \frac{D_\perp}{\omega_\ast\,w^2}.
\end{align}
Finally,
\begin{equation}
\frac{1}{L_n}= -\frac{1}{{\mit\Gamma}\,(1-c_\beta^{\,2})}\left(\frac{d\ln n}{dr}\right)_{r_s}
\end{equation}
is the {\em density gradient scalelength}\/  at the resonant surface, 
and the critical reduced island width, $w_c$, is defined in Equation~(\ref{wcdef}).

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{align}
In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.
